Msc Thesis Figures

### 2020-08-01 docs/msc_thesis_figures.tex
move to docs

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{theme_set}\NormalTok{(}\KeywordTok{theme_minimal}\NormalTok{())}
\KeywordTok{theme_update}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.85}\NormalTok{, }\FloatTok{0.20}\NormalTok{),}
             \CommentTok{#legend.justification = c(1, -0.2), # for inside plot}
             \CommentTok{#legend.position = "none",}
             \DataTypeTok{legend.box =} \StringTok{"vertical"}\NormalTok{,}
             \DataTypeTok{legend.background =} \KeywordTok{element_blank}\NormalTok{(),}
             \DataTypeTok{legend.box.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \StringTok{"black"}\NormalTok{),}
             \DataTypeTok{panel.border =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{fill =} \OtherTok{NA}\NormalTok{),}
             \DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{8}\NormalTok{),}
             \DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{plot.subtitle =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{axis.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{65}\NormalTok{, }\DataTypeTok{vjust=}\FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\DecValTok{13}\NormalTok{),}
             \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =}\DecValTok{10}\NormalTok{),}
             \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{axis.title=}\KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{15}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fig_}\DecValTok{1}\NormalTok{_historic <-}\StringTok{ }\NormalTok{joined }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(climate }\OperatorTok{==}\StringTok{ "none"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(scenarioId, species, iteration) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_modify}\NormalTok{(}\OperatorTok{~}\KeywordTok{mutate}\NormalTok{(.x , }\DataTypeTok{baseline =} \KeywordTok{subset}\NormalTok{(.x, timestep }\OperatorTok{==}\StringTok{ }\DecValTok{1990}\NormalTok{)}\OperatorTok{$}\NormalTok{sum_cur, }
                       \DataTypeTok{the_diff =}\NormalTok{ ((sum_cur}\OperatorTok{-}\NormalTok{baseline)}\OperatorTok{/}\NormalTok{baseline)}\OperatorTok{*}\DecValTok{100}\NormalTok{ )) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{timestep, }\DataTypeTok{y=}\NormalTok{the_diff, }\DataTypeTok{col=}\NormalTok{source)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_color_manual}\NormalTok{(}\DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{'#d8b365'}\NormalTok{,}\StringTok{'#5ab4ac'}\NormalTok{), }
                     \DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Model"}\NormalTok{, }\StringTok{"Observation"}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{group =}\NormalTok{ sce), }\DataTypeTok{method =} \StringTok{"glm"}\NormalTok{, }\DataTypeTok{se=}\OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_linetype_manual}\NormalTok{(}\DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{5}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{group =}\NormalTok{ sce)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{species, }\DataTypeTok{scales =} \StringTok{"free"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Current flow (% Change)"}\NormalTok{,}
       \DataTypeTok{x =} \StringTok{"Year"}\NormalTok{,}
       \DataTypeTok{col =} \StringTok{"Source"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\OtherTok{NULL}
\NormalTok{fig_}\DecValTok{1}\NormalTok{_historic}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_historic,}
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_historic.png"}\NormalTok{,}
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{1}\NormalTok{, }
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_chap1.png"}\NormalTok{, }
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_chap1 <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_chap1, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size   =}\DecValTok{3}\NormalTok{)}
\NormalTok{radar_chap1}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{2}\NormalTok{, }
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_chap2.png"}\NormalTok{, }
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_chap2 <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_chap2, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size   =}\DecValTok{3}\NormalTok{)}
\NormalTok{radar_chap2}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_all <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_all, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size   =}\DecValTok{3}\NormalTok{)}
\NormalTok{radar_all}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{hist_plot_}\DecValTok{1}\NormalTok{ <-}\StringTok{ }\NormalTok{histograms }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ts =} \KeywordTok{as.factor}\NormalTok{(ts)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(chapter }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{'both'}\NormalTok{, }\StringTok{'chap_1'}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{bins, }\DataTypeTok{y=}\NormalTok{n, }\DataTypeTok{group=}\NormalTok{ts, }\DataTypeTok{colour=}\NormalTok{ts)) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{geom_density}\NormalTok{(}\DataTypeTok{stat=}\StringTok{'identity'}\NormalTok{, }\DataTypeTok{show.legend=}\NormalTok{F, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{fill=}\KeywordTok{factor}\NormalTok{(ts)), }\DataTypeTok{alpha=}\FloatTok{0.3}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(code}\OperatorTok{~}\NormalTok{species) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Flow intensity distribution (log)"}\NormalTok{, }
       \DataTypeTok{y =} \StringTok{""}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{360}\NormalTok{, }\DataTypeTok{size=}\DecValTok{10}\NormalTok{, }\DataTypeTok{hjust =} \DecValTok{0}\NormalTok{), }
        \DataTypeTok{axis.text.x=}\KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.ticks.x=}\KeywordTok{element_blank}\NormalTok{(), }
        \DataTypeTok{axis.text.y.left =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.ticks.y.left =} \KeywordTok{element_blank}\NormalTok{()) }\OperatorTok{+}
\StringTok{  }\OtherTok{NULL}
\NormalTok{hist_plot_}\DecValTok{1}
\end{Highlighting}
\end{Shaded}

\includegraphics[width=1\linewidth,height=1.5\textheight]{msc_thesis_figures_files/figure-latex/hist_plot_1-1}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{hist_plot_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\NormalTok{histograms }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ts =} \KeywordTok{as.factor}\NormalTok{(ts)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(chapter }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{'both'}\NormalTok{, }\StringTok{'chap_2'}\NormalTok{)) }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{bins, }\DataTypeTok{y=}\NormalTok{n, }\DataTypeTok{group=}\NormalTok{ts, }\DataTypeTok{colour=}\NormalTok{ts)) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{geom_density}\NormalTok{(}\DataTypeTok{stat=}\StringTok{'identity'}\NormalTok{, }\DataTypeTok{show.legend=}\NormalTok{F, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{fill=}\KeywordTok{factor}\NormalTok{(ts)), }\DataTypeTok{alpha=}\FloatTok{0.3}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(code}\OperatorTok{~}\NormalTok{species) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Flow intensity distribution (log)"}\NormalTok{, }
       \DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{360}\NormalTok{, }\DataTypeTok{size=}\DecValTok{10}\NormalTok{, }\DataTypeTok{hjust =} \DecValTok{0}\NormalTok{), }
        \DataTypeTok{axis.text.x=}\KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.ticks.x=}\KeywordTok{element_blank}\NormalTok{(), }
        \DataTypeTok{axis.text.y.left =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.ticks.y.left =} \KeywordTok{element_blank}\NormalTok{()) }\OperatorTok{+}
\StringTok{  }\OtherTok{NULL}
\NormalTok{hist_plot_}\DecValTok{2}
\end{Highlighting}
\end{Shaded}

\includegraphics[width=1\linewidth]{msc_thesis_figures_files/figure-latex/hist_plot_2-1}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{theme_set}\NormalTok{(}\KeywordTok{theme_minimal}\NormalTok{())}
\KeywordTok{theme_update}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.85}\NormalTok{, }\FloatTok{0.20}\NormalTok{),}
             \DataTypeTok{legend.box =} \StringTok{"vertical"}\NormalTok{,}
             \DataTypeTok{legend.background =} \KeywordTok{element_blank}\NormalTok{(),}
             \DataTypeTok{legend.box.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \StringTok{"black"}\NormalTok{),}
             \DataTypeTok{panel.border =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{fill =} \OtherTok{NA}\NormalTok{),}
             \DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{15}\NormalTok{),}
             \DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{13}\NormalTok{),}
             \DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{plot.subtitle =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{axis.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{65}\NormalTok{, }\DataTypeTok{vjust=}\FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\DecValTok{13}\NormalTok{),}
             \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =}\DecValTok{13}\NormalTok{),}
             \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{13}\NormalTok{),}
             \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DecValTok{13}\NormalTok{),}
             \DataTypeTok{axis.title=}\KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{18}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fig_}\DecValTok{1}\NormalTok{_historic <-}\StringTok{ }\NormalTok{joined }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(climate }\OperatorTok{==}\StringTok{ "none"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(scenarioId, species, iteration) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_modify}\NormalTok{(}\OperatorTok{~}\KeywordTok{mutate}\NormalTok{(.x , }\DataTypeTok{baseline =} \KeywordTok{subset}\NormalTok{(.x, timestep }\OperatorTok{==}\StringTok{ }\DecValTok{1990}\NormalTok{)}\OperatorTok{$}\NormalTok{sum_cur, }
                       \DataTypeTok{the_diff =}\NormalTok{ ((sum_cur}\OperatorTok{-}\NormalTok{baseline)}\OperatorTok{/}\NormalTok{baseline)}\OperatorTok{*}\DecValTok{100}\NormalTok{ )) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{timestep, }\DataTypeTok{y=}\NormalTok{the_diff, }\DataTypeTok{col=}\NormalTok{source)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_color_manual}\NormalTok{(}\DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{'#d8b365'}\NormalTok{,}\StringTok{'#5ab4ac'}\NormalTok{), }
                     \DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Model"}\NormalTok{, }\StringTok{"Observation"}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{group =}\NormalTok{ sce), }\DataTypeTok{method =} \StringTok{"glm"}\NormalTok{, }\DataTypeTok{se=}\OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_linetype_manual}\NormalTok{(}\DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{2}\NormalTok{,}\DecValTok{5}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{group =}\NormalTok{ sce)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{species, }\DataTypeTok{scales =} \StringTok{"fixed"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Current flow (% Change)"}\NormalTok{,}
       \DataTypeTok{x =} \StringTok{"Year"}\NormalTok{,}
       \DataTypeTok{col =} \StringTok{"Source"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\OtherTok{NULL}
\NormalTok{fig_}\DecValTok{1}\NormalTok{_historic}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database

## Warning in grid.Call(C_stringMetric, as.graphicsAnnot(x$label)): font family
## '13' not found in PostScript font database
\end{verbatim}

\begin{verbatim}
## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_historic,}
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_historic.png"}\NormalTok{,}
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{15}\NormalTok{, }\DataTypeTok{dpi =} \DecValTok{500}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database

## Warning in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, : font
## family '13' not found in PostScript font database
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{1}\NormalTok{, }
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_chap1.png"}\NormalTok{, }
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{15}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_chap1 <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_chap1, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size=}\DecValTok{5}\NormalTok{)}
\NormalTok{radar_chap1}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{2}\NormalTok{, }
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_chap2.png"}\NormalTok{, }
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{15}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_chap2 <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_chap2, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size=}\DecValTok{5}\NormalTok{)}
\NormalTok{radar_chap2}
\end{Highlighting}
\end{Shaded}

@@

\NormalTok{radar_all <-}\StringTok{  }
\StringTok{  }\KeywordTok{ggradar}\NormalTok{(radar_data_all, }\DataTypeTok{centre.y =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{legend.position =} \StringTok{"right"}\NormalTok{,}
          \DataTypeTok{grid.min =} \DecValTok{-20}\NormalTok{, }\DataTypeTok{grid.max =} \DecValTok{3}\NormalTok{, }\DataTypeTok{grid.mid =} \DecValTok{0}\NormalTok{, }
          \DataTypeTok{values.radar =} \KeywordTok{c}\NormalTok{(}\StringTok{"-20 %"}\NormalTok{, }\StringTok{"0 %"}\NormalTok{, }\StringTok{""}\NormalTok{), }
          \DataTypeTok{gridline.label.offset =}\DecValTok{5}\NormalTok{, }\DataTypeTok{legend.text.size=} \DecValTok{12}\NormalTok{,}
          \DataTypeTok{group.line.width =}\FloatTok{0.8}\NormalTok{,}
          \DataTypeTok{background.circle.colour  =} \StringTok{"#ffffff"}\NormalTok{, }\DataTypeTok{group.point.size   =} \DecValTok{2}\NormalTok{, }
          \DataTypeTok{axis.label.size=}\DecValTok{5}\NormalTok{)}
\NormalTok{radar_all}
\end{Highlighting}
\end{Shaded}

@@

@@
